|

### 2025-05-05 doc/paper.qmd
Inserted formula

## Results {#sec-results1}
This section presents the replication results, comparing them with the original @ by @ball_how_2008.

@@

## Results {#sec-results2}
Shifting the sample to 2007–2023 introduces potential changes in earnings announcement informativeness driven by key economic and regulatory events. The 2008 financial crisis and the 2020 COVID-19 pandemic likely heightened market uncertainty, increasing reliance on earnings disclosures to assess firm stability. Moreover, Regulation (EU) No 537/2014 may have enhanced financial reporting transparency and audit quality in EU countries, potentially affecting how earnings news is reflected in stock prices and contributing to cross-country variation in informativeness.

@@

>>>>

## Results {#sec-results1}
This section presents the replication results, comparing them with the original @fig-fig1_original by @ball_how_2008.

```{r}
#| label: fig-fig1_original
#| fig-cap: "Original Figure 1 from Ball and Shivakumar (2008)"
#| echo: false
#| fig-align: center
knitr::include_graphics("fig1_original.pdf")
```

@@

## Results {#sec-results2}
Shifting the sample to 2007–2023 introduces potential changes in earnings announcement informativeness driven by key economic events. The 2008 financial crisis and the 2020 COVID-19 pandemic likely heightened market uncertainty, increasing reliance on earnings disclosures to assess firm stability. These developments may have influenced how earnings news is reflected in stock prices and contributed to variation in informativeness across countries.

@@

Specifically, buy-and-hold return over the three-day event window, that measures the stock’s reaction only to earnings news, is computed as given below:
$$
\begin{aligned}
BHR_{\text{event}} &= (1 + R_{t_1}) (1 + R_{t_2}) \dots (1 + R_{t_T}) - 1,
\\
\text{where } R_t & \text{ is the daily return and } T \text{ is the total trading days in a year.}
\end{aligned}
$$
